Holomorphic field theories and higher algebra

### 2022-08-24 draft.tex
edited section on fact algs

@@

This theorem applies to many well-known examples from physics, such as 
\begin{itemize}
\item the topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies);
\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook});
\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi}; and
\item the Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW},
\end{itemize}
among other examples of topological AKSZ theories, such as BF theories.
In all these examples, the underlying elliptic complex is a version of the de Rham complex.

@@

@@

\begin{dfn}
The {\em $d$-polydiscs dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
and where there is a dg vector space of $n$-ary cooperations
\[
\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) 
\]
for any list of radii $r_1,\ldots, r_n, R$.
There is a composition
\[
\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R))\to \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
\]
only when $r_i = S$, 
and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
(Composition is not defined if the radii do not match.)
\end{dfn}

An algebra $A$ over this cooperad means that for each radius~$r$, 
there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
there is a cochain map
\[
\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) .
\]
To invest the map $\alpha$ with more meaning, 
pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
For instance, for any inputs $a_i \in A(r_i)$ and any cocycle $\omega \in \Omega^{0,k}(\PDisc_d(r_1, \ldots, r_n| R))$, we get an element in $A(R)$~by
\[
\int_T \alpha(a_1 \otimes \cdots \otimes a_n) \wedge \omega,
\]
where we have suppressed distracting notation from~$\alpha$.

@@

A key idea for us is that much of the content in field theories --- both classical and quantum --- is captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
With the notion in hand, we will describe several examples and several situations where factorization algebras have already appeared in mathematics and physics, 
albeit in a different formulation.
Finally, we will sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.

@@

Let $M$ be a topological space and let $\mc{C}^\otimes$ be a symmetric monoidal category. 
In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.

A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
\begin{itemize}
\item  There is a cochain map $m_V^U: \cF(U) \rightarrow \cF(V)$ for each inclusion $U \subset V$.

@@

\item The maps are compatible in the obvious way, so that if $U_{i,1}\sqcup\cdots\sqcup U_{i,n_i}\subseteq V_i$ and $V_1\sqcup\cdots\sqcup V_k\subseteq W$, the following diagram commutes.
\begin{center}
\begin{tikzcd}[column sep=small]
{\bigotimes}^{k}_{i=1}{\bigotimes}^{n_i}_{j=1}\cF(U_j) \arrow{dr} \arrow{rr} &   &{\bigotimes}^k_{i=1}\cF(V_i) \arrow{dl}\\
&\cF(W)  &
\end{tikzcd}
\end{center}
\end{itemize}

@@

This definition bears analogies to familiar objects in mathematics.
On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
(A presheaf is a functor out of the opposite category to opens in $M$.) 
Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
This feature leads to the other analogy: $\cF$ resembles an algebra, as
the multilinear maps look like multiplications.
These maps let us multiply elements from disjoint regions to get an element in a larger region.

Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
We say that $\cF$ is a \emph{unital} prefactorization algebra  if $\cF(\emptyset)$ is a unital commutative algebra. In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$. In practice, for our examples, $\cF(\emptyset)$ is $\CC$, $\RR$, $\CC[[\hbar]]$, or $\RR[[\hbar]]$.

\begin{eg}\label{ex:associativealgebra}
The crucial example to bear in mind is an associative algebra. Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows. To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$. To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. The structure maps simply arise from the multiplication map for $A$. Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$. Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra. 
%(One takes an infinite tensor products of unital algebras, as follows. Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion. For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$. For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$. Then $A^I$ is the colimit over this poset.) 
~\hfill$\Diamond$
\end{eg}

@@

We will now sketch another way of phrasing this idea, but the reader who is content with this definition and eager to see examples should feel free to jump ahead, referring back as needed.

\subsection{Prefactorization algebras as algebras over an operad}
\label{sec:disj}

The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
See \owen{add citations}

\begin{dfn}
Let $\Disj_M$ denote the following colored operad associated to~$M$: 
\begin{itemize}
\item The colors (or objects) consist of all open subsets of $M$. 
\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$. If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point. Otherwise, the set of maps is empty.
\item The composition of maps is defined in the obvious way. 
\end{itemize}
\end{dfn}

\begin{dfn}
Let $\mc{C}$ be a colored operad. 
A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
\end{dfn}

In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories.

\begin{rmk} 
If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
~\hfill$\Diamond$ 
\end{rmk}

Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$.

\begin{dfn}
We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
\end{dfn}

\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
\label{AssAsFact}

We explained above how an associative algebra provides a prefactorization algebra on the real line. There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras. Here we will characterize those that do arise from associative algebras.

\begin{dfn}
Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
\end{dfn}

It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.

\begin{lem}\label{locally_constant_is_associative}
Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
\end{lem}

One can got further, however, and also capture modules, essentially by marking the line with points.
For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.

Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$. 
We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure.

Pick a point $p \in \RR$. On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$. Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$. Intervals containing $p$ are determined, though, by $M$. When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$. The structure maps are also determined by the bimodule structure. For example, given 
\[
s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
\]
we have
\begin{align*}
\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
&= A \ot M \ot B
\end{align*}
and the inclusion of these three intervals into $(s_0,u_1)$ is the map
\[
\begin{array}{ccc}
\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
a \ot m \ot b & \mapsto & amb
\end{array}.
\]
The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.

%\begin{figure}
%\begin{center}
% \begin{minipage}{3cm}
% \begin{tikzpicture}[scale=0.75]
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,0) -- (-1.5,0); 
% \draw (-1,0) -- (0.5,0); 
% \draw[fill=black] (0,0) circle (0.07);
% \draw (1.5,0) -- (2.5,0); 
% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
% \draw (-2.75,-2) -- (0.75,-2); 
% \draw[fill=black] (0,-2) circle (0.07);
% \draw (1.25,-2) -- (2.75,-2);  
% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
% \draw (-3,-4) -- (3,-4);
% \draw[fill=black] (0,-4) circle (0.07); 
% \end{scope}
% \end{tikzpicture}
% \end{minipage}
%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
% \begin{minipage}{8cm}
% \begin{tikzcd}[cramped,column sep=tiny]
%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
%amb  & \in &M 
%\end{tikzcd}
%\end{minipage}
%\end{center}
%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
%\label{fig:bimodasfact}
%\end{figure}

\begin{figure}
\begin{center}
 \begin{tikzpicture}
 \begin{scope}[line cap=round,ultra thick]
 \draw (-2.5,1) -- (-1.5,1); 
 \draw (-1,1) -- (0.5,1); 
 \draw[fill=black] (0,1) circle (0.07);
 \draw (1.5,1) -- (2.5,1); 
 \draw[->,semithick] (0,0.75) -- (0,0.25);
 \draw (-2.75,-0.1) -- (0.75,-0.1); 
 \draw[fill=black] (0,-0.1) circle (0.07);
 \draw (1.25,-0.1) -- (2.75,-0.1);  
 \draw[->,semithick] (0,-0.35) -- (0,-0.85);
 \draw (-3,-1.2) -- (3,-1.2);
 \draw[fill=black] (0,-1.2) circle (0.07); 
 \end{scope}

\node at (4,0){$\rightsquigarrow$};

\node at (7,0) {
\begin{tikzcd}[cramped,column sep=tiny]
a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
amb  & \in &M 
\end{tikzcd}
};

\end{tikzpicture}
\end{center}
\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
\label{fig:bimodasfact}
\end{figure}

@@

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$.

\begin{rmk}
A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens. It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$. For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection 
\[
\{ U_i^n \mid i \in I\}
\]
provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
\end{rmk}

>>>>

This operad was invented by algebraic topologists to capture the rich structure of the $d$-fold based loop space $\Omega^d X$ of a pointed space $(X,x)$.
(The usual homotopy group $\pi_d(X)$ is a shadow of this richer structure.)
Thus there is a deep reservoir of tools and results for studying algebras over the little discs operads in algebraic topology.

@@

\owen{Actually say what kind of $d$-discs algebras one gets.}
This theorem applies to many well-known examples from physics:
\begin{itemize}
\item The topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold $X$ (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies) yields an $E_2$ algebra. It is quasi-isomorphic to the well-known Gerstenhaber algebra of polyvector fields on~$X$.
\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook}) yields an $E_3$ algebra, which encodes the quantum group $U_\hbar \fg$ under a version of Koszul duality.
\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi} yields an $E_3$ algebra \owen{on what?}
\item Each Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW} yields an $E_4$ algebra, related to deforming the coadjoint quotient stack~$\fg^*/G$.
\end{itemize}
It applies to other examples of topological AKSZ theories, such as BF theories.
In all these examples, the underlying elliptic complex is a version of the de Rham complex.

@@

This theorem builds an explicit bridge between topology and physics. 
Thanks to the theorem of Elliott and Safronov, we know that most topological field theories in the physicist's sense provide $E_n$ algebras,
but they can thus be analyzed using the powerful machinery of modern homotopy theory. 
Conversely, intuition from physics about the behavior of topological field theories suggests novel constructions and examples to topology. 
Much of the amazing resonance between operads, homological algebra, and string-theoretic physics over the last few decades can be understood from this perspective.

@@

\begin{dfn}
\label{dfn pdisc}
The {\em $d$-polydiscs dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
and where there is a dg vector space of $n$-ary cooperations
\[
\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) 
\]
for any list of radii $r_1,\ldots, r_n, R$.
There is a composition
\[
\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R))\to \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
\]
only when $r_i = S$, 
and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisc into an input polydisc of the same radius.
(Composition is not defined if the radii do not match.)
\end{dfn}

\owen{Improve!}
An algebra $A$ over this cooperad means that for each radius~$r$, 
there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
there is a cochain map
\[
\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) .
\]
To invest the map $\alpha$ with more meaning, 
pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
\[
\int_T \alpha(a_1 \otimes \cdots \otimes a_n),
\]
where we have suppressed distracting notation from~$\alpha$.

@@

A key idea for us is that much of the content in field theories --- both classical and quantum --- is captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
Their local structure encompasses the behavior we saw in the preceding section, where $E_d$ algebras captured topological field theories on $\RR^d$ and $\PDisc_d$ algebras captured holomorphic field theories on~$\CC^d$.
Factorization algebras allow one to work on smooth manifolds, and complex manifolds, more generally;
their global behavior encompasses constructions like Hochschild homology and conformal blocks.
We will then sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.
Finally, we describe some special features and interesting applications of factorization algebras of holomorphic field theories.

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of smooth manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by all this work, Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
\end{rmk}

@@

Let $M$ be a topological space and let $\mc{C}^\otimes$ be a symmetric monoidal category. 
In this paper $M$ is always a smooth manifold (typically a complex manifold) and $\mc{C}$ is ${\rm Vect}$ or ${\rm dgVect}$, with the usual tensor product as the symmetric monoidal product.
(As mentioned in the paragraph before Definition~\ref{dfn pdisc}, one needs to deal with issues of functional analysis for applications to QFT, but we will not discuss those aspects here.
In brief, for purposes of holomorphic field theories, we use an $\infty$-category obtained from working with cochain complexes of differentiable vector spaces, with extensive treatment in~\cite{CG1}.)

\begin{dfn}
A {\em prefactorization algebra} $\cF$ on $M$ taking values in cochain complexes is a rule that assigns a cochain complex $\cF(U)$ to each open set $U \subset M$ along with the following maps and compatibilities.
\begin{itemize}
\item  There is a cochain map $m_V^U: \cF(U) \rightarrow \cF(V)$ for each inclusion $U \subset V$.

@@

\item The maps are compatible in the obvious way, so that if $U_{i,1}\sqcup\cdots\sqcup U_{i,n_i}\subseteq V_i$ and $V_1\sqcup\cdots\sqcup V_k\subseteq W$, the following diagram commutes.
\begin{center}
\begin{tikzcd}[column sep=small]
{\bigotimes}^{k}_{i=1}{\bigotimes}^{n_i}_{j=1}\cF(U_j) \arrow{dr} \arrow{rr} &   &{\bigotimes}^k_{i=1}\cF(V_i) \arrow{dl}\\
&\cF(W)  &
\end{tikzcd}
\end{center}
\end{itemize}
\end{dfn}

@@

This definition bears analogies to familiar objects in mathematics.
On the one hand, $\cF$ resembles a {\em precosheaf}, which is a functor from opens in $M$ to a category like ${\rm Vect}$ or ${\rm dgVect}$.
(A presheaf is a functor out of the opposite category to opens in~$M$.) 
Here, however, $\cF$ also assign values to disjoint unions of opens, and it uses the tensor product rather than direct sum.
This feature leads to the other analogy: $\cF$ resembles an algebra, as
the multilinear maps look like multiplications.
These maps let us multiply elements from disjoint regions to get an element in a larger region.

%Note that these axioms imply that $\cF(\emptyset)$ is a commutative algebra. 
%We say that $\cF$ is a \emph{unital} prefactorization algebra if $\cF(\emptyset)$ is a unital commutative algebra. In this case, $\cF(U)$ is a pointed cochain complex by the image of the unit $1 \in \cF(\emptyset)$ under the structure map $\cF(\emptyset) \to \cF(U)$. In practice, for our examples, $\cF(\emptyset)$ is $\CC$, $\RR$, $\CC[[\hbar]]$, or $\RR[[\hbar]]$.

\begin{eg}\label{ex:associativealgebra}
Every associative algebra $A$ defines a prefactorization algebra $\cF_A$ on $\RR$, as follows. To each open interval $(a,b)$, we set $\cF_A( (a,b) ) = A$. To any open set $U = \coprod_j I_j$, where each $I_j$ is an open interval, we set $\cF(U) = \bigotimes_j A$. The structure maps simply arise from the multiplication map for $A$. Figure ~\ref{fig:assasfact} displays the structure of $\cF_A$. Notice the resemblance to the notion of an $E_1$ or $A_\infty$ algebra. 
%(One takes an infinite tensor products of unital algebras, as follows. Given an infinite set $I$, consider the poset of finite subsets of $I$, ordered by inclusion. For each finite subset $J \subset I$, we can take the tensor product $A^J = \bigotimes_{j \in J} A$. For $J \hookrightarrow J'$, we define a map $A^J \to A^{J'}$ by tensoring with the identity $1 \in A$ for every $j \in J' \backslash J$. Then $A^I$ is the colimit over this poset.) 
~\hfill$\Diamond$
\end{eg}

@@

There is another, more sophisticated way to phrase prefactorization algebras, using the framework of operads.
Associated to each topological space $M$, there is a colored operad $\Disj_M$ such that a prefactorization algebra is an algebra over~$\Disj_M$.
For a discussion, see Chapter 3 of~\cite{CG1};
related ideas are developed in~\cite{AF, LurieHA, Ginot}.

%\subsection{Prefactorization algebras as algebras over an operad}
%\label{sec:disj}
%
%The language of colored operads offers a convenient way to formalize the notion of prefactorization algebra.
%A colored operad is a generalization of the idea of a category, where one allows many-to-one maps, and so the term ``multicategory'' is sometimes used. 
%See \owen{add citations}
%
%\begin{dfn}
%Let $\Disj_M$ denote the following colored operad associated to~$M$: 
%\begin{itemize}
%\item The colors (or objects) consist of all open subsets of $M$. 
%\item For every (possibly empty) finite collection of open sets $\{U_\alpha\}_{\alpha \in A}$ and open set $V$, there is a set of maps $\Disj_M( \{U_\alpha\}_{\alpha \in A} \mcol V)$. If the $U_\alpha$ are pairwise disjoint and all are contained in $V$, then the set of maps is a single point. Otherwise, the set of maps is empty.
%\item The composition of maps is defined in the obvious way. 
%\end{itemize}
%\end{dfn}
%
%\begin{dfn}
%Let $\mc{C}$ be a colored operad. 
%A \emph{prefactorization algebra}  on $M$ taking values in $\mc{C}$ is a map of colored operads from $\Disj_M$ to~$\mc{C}$. 
%\end{dfn}
%
%In other words, a prefactorization algebra \emph{is} an algebra over the colored operad $\Disj_M$.
%Since symmetric monoidal categories are special kinds of multicategories, this definition makes sense for symmetric monoidal categories. 
%
%\begin{rmk} 
%If $\mc{C}$ is a symmetric monoidal category under coproduct, then a precosheaf on $M$ with values in $\mc{C}$ defines a prefactorization algebra valued in $\mc{C}$. 
%Hence, our definition broadens the idea of ``inclusion of open sets leads to inclusion of sections'' by allowing more general monoidal structures to ``combine'' the sections on disjoint open sets.
%~\hfill$\Diamond$ 
%\end{rmk}
%
%Note that if $\cF$ is any prefactorization algebra, then $\cF(\emptyset)$ is a commutative algebra object of $\mc{C}$. 
%
%\begin{dfn}
%We say a prefactorization algebra $\cF$ is \emph{unital} if the commutative algebra $\cF(\emptyset)$ is unital. 
%\end{dfn}
%
%\subsection{Encoding ordinary algebras and modules using prefactorization algebras on $\RR$}
%\label{AssAsFact}
%
%We explained above how an associative algebra provides a prefactorization algebra on the real line. There are, however, prefactorization algebras on $\RR$ that do {\em not} come from associative algebras. Here we will characterize those that do arise from associative algebras.
% 
%\begin{dfn}
%Let $\cF$ be a prefactorization algebra on $\RR$ taking values in the category of vector spaces (without any grading).   
%We say $\cF$ is \emph{locally constant} if the map $\cF(U) \to \cF(V)$ is an isomorphism for any  inclusion of open intervals $U \subset V$. 
%\end{dfn}
%
%It is an illuminating exercise to check that this property ensures a prefactorization algebra encodes an associative algebra.
%
%\begin{lem}\label{locally_constant_is_associative}
%Let $\cF$ be a locally constant, unital prefactorization algebra on $\RR$ taking values in vector spaces. 
%Let $A = \cF(\RR)$. Then $A$ has a natural structure of an associative algebra.  
%\end{lem}
%
%One can got further, however, and also capture modules, essentially by marking the line with points.
%For simplicity, we will continue to work with ordinary vector spaces with the tensor product as symmetric monoidal structure.
%
%Let $A$ and $B$ be associative algebras and $M$ an $A-B$-bimodule, i.e., $M$ is a left $A$-module and a right $B$-module and these structures are compatible in that $(am)b = a(mb)$ for all $a \in A$, $b \in B$, and $m \in M$. 
%We now construct a prefactorization algebra $\cF_M$ on $\RR$ that encodes this bimodule structure. 
%
%Pick a point $p \in \RR$. On the half-line $\{x \in \RR \mid x < p\}$, $\cF_M$ is given by $\cF_A$: to an interval $I = (t_0,t_1)$ with $t_1 <p$, $\cF_M(I) = A$, and the structure map for inclusion of finitely many disjoint intervals into a bigger interval is determined by multiplication in $A$. Likewise, on the half-line $\{x \in \RR \mid p < x\}$, $\cF_M$ is given by $\cF_B$. Intervals containing $p$ are determined, though, by $M$. When we consider an interval $I = (t_0,t_1)$ such that $t_0 < p < t_1$, we set $\cF_M(I)  = M$. The structure maps are also determined by the bimodule structure. For example, given 
%\[
%s_0 < s_1 < t_0 < p < t_1 < u_0 < u_1,
%\]
%we have
%\begin{align*}
%\cF_M((s_0,s_1) \sqcup (t_0, t_1) \sqcup (u_0 , u_1)) 
%&= \cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) \\
%&= A \ot M \ot B
%\end{align*}
%and the inclusion of these three intervals into $(s_0,u_1)$ is the map
%\[
%\begin{array}{ccc}
%\cF_M((s_0,s_1)) \ot \cF_M((t_0, t_1)) \ot \cF_M((u_0 , u_1)) & \to & \cF_M((s_0,u_1)) \\
%a \ot m \ot b & \mapsto & amb
%\end{array}.
%\]
%The definition of a bimodule ensures that we have a prefactorization algebra. See Figure ~\ref{fig:bimodasfact}.
%
%%\begin{figure}
%%\begin{center}
%% \begin{minipage}{3cm}
%% \begin{tikzpicture}[scale=0.75]
%% \begin{scope}[line cap=round,ultra thick]
%% \draw (-2.5,0) -- (-1.5,0); 
%% \draw (-1,0) -- (0.5,0); 
%% \draw[fill=black] (0,0) circle (0.07);
%% \draw (1.5,0) -- (2.5,0); 
%% \draw[->,semithick] (0,-0.5) -- (0,-1.5);
%% \draw (-2.75,-2) -- (0.75,-2); 
%% \draw[fill=black] (0,-2) circle (0.07);
%% \draw (1.25,-2) -- (2.75,-2);  
%% \draw[->,semithick] (0,-2.5) -- (0,-3.5);
%% \draw (-3,-4) -- (3,-4);
%% \draw[fill=black] (0,-4) circle (0.07); 
%% \end{scope}
%% \end{tikzpicture}
%% \end{minipage}
%%\hspace{2cm} $\rightsquigarrow$ \hspace{0.5cm}
%% \begin{minipage}{8cm}
%% \begin{tikzcd}[cramped,column sep=tiny]
%%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
%%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
%%amb  & \in &M 
%%\end{tikzcd}
%%\end{minipage}
%%\end{center}
%%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
%%\label{fig:bimodasfact}
%%\end{figure}
%
%\begin{figure}
%\begin{center}
% \begin{tikzpicture}
% \begin{scope}[line cap=round,ultra thick]
% \draw (-2.5,1) -- (-1.5,1); 
% \draw (-1,1) -- (0.5,1); 
% \draw[fill=black] (0,1) circle (0.07);
% \draw (1.5,1) -- (2.5,1); 
% \draw[->,semithick] (0,0.75) -- (0,0.25);
% \draw (-2.75,-0.1) -- (0.75,-0.1); 
% \draw[fill=black] (0,-0.1) circle (0.07);
% \draw (1.25,-0.1) -- (2.75,-0.1);  
% \draw[->,semithick] (0,-0.35) -- (0,-0.85);
% \draw (-3,-1.2) -- (3,-1.2);
% \draw[fill=black] (0,-1.2) circle (0.07); 
% \end{scope}
%
%\node at (4,0){$\rightsquigarrow$};
%
%\node at (7,0) {
%\begin{tikzcd}[cramped,column sep=tiny]
%a \otimes m \otimes b \arrow[mapsto]{d} & \in & A \otimes M \otimes B \arrow{d} \\
%am \otimes b \arrow[mapsto]{d} & \in & M \otimes B \arrow{d} \\
%amb  & \in &M 
%\end{tikzcd}
%};
%
%\end{tikzpicture}
%\end{center}
%\caption{The prefactorization algebra $\cF_M$ for the $A-B$-bimodule $M$}
%\label{fig:bimodasfact}
%\end{figure}

@@

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
and so they often contain many opens.
For a smooth $n$-manifold $M$, one cover is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.

%\begin{rmk}
%A Weiss cover is certainly a cover in the usual sense, but a Weiss cover typically contains an enormous number of opens. It is a kind of ``exponentiation" of the usual notion of cover, because a Weiss cover is well-suited to studying all configuration spaces of finitely many points in $U$. For instance, given a Weiss cover $\mathfrak{U}$ of $U$, the collection 
%\[
%\{ U_i^n \mid i \in I\}
%\]
%provides a cover in the usual sense of $U^n \subset M^n$ for every positive integer~$n$.\hfill$\Diamond$ 
%\end{rmk}
%
%\begin{eg}\label{WeissAsExponential}
%For a smooth $n$-manifold $M$, there are several simple ways to construct a Weiss cover for $M$. One construction is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc. Alternatively, the collection of opens $\{ M \setminus q \mcol q \in M\}$ is a Weiss cover of $M$. One can also produce a Weiss cover of a manifold with countably many elements. Fix a Riemannian metric on $M$. Pick a collection of points $\{q_n\in M \mcol n \in \NN\}$ such that the union of the unit ``discs'' $D_1(q_n) = \{ q \in M \mcol \d(q_n,q) < 1\}$ covers $M$. (Such an open may not be homeomorphic to a disc if the injectivity radius of $q_n$ is less than 1.)  Consider the collection of all ``discs'' $\fD = \{ D_{1/m}(q_n) \mcol m \in \NN, n \in \NN\}$.  The collection of all finite, pairwise disjoint union of elements of $\fD$ is a countable Weiss cover.~\hfill $\Diamond$ 
%\end{eg}

Now that we have a notion of cover, we can formulate the local-to-global property for factorization algebras.

\begin{dfn}
A \emph{factorization algebra} is a prefactorization algebra $\cF$ on $M$ with values in a symmetric monoidal category $\cC^\otimes$ that is a cosheaf for the Weiss topology.
\end{dfn}
